### 2015-04-21 paper.tex
Space in figure caption
Cite Re dep paper to be submitted

For example, the effect of Reynolds number on average power output was shown to
be significant on the 2 m Sandia Research Darrieus turbine in wind tunnel
testing \cite{Blackwell1976}: Maximum power coefficient, $C_{P,\mathrm{max}}$,
increased with Reynolds number, $Re_c$, along with a shift of the location of
$C_{P,\mathrm{max}}$ toward lower tip speed ratios due to delayed blade stall.
The effects of Reynolds number were quite dramatic over a relatively small range
of $Re_c \approx 1.1 \times 10^5$--$2.9 \times 10^5$. More recently, Bachant and
Wosnik \cite{Bachant2014} showed that turbine performance and near-wake
characteristics become Reynolds number independent at $Re_c \approx 2 \times
10^5$.

@@

\begin{table}[ht]
\centering
\begin{tabular}{c|c|c}
Tow speed (m/s) & $Re_D$ & $Re_c$ at $\lambda = 3$ \\ 
\hline 
0.2 & $2.2 \times 10^5$ & $4.0 \times 10^4$ \\ 
0.4 & $4.3 \times 10^5$ & $8.0 \times 10^4$ \\ 
0.6 & $6.5 \times 10^5$ & $1.2 \times 10^5$ \\ 
0.8 & $8.6 \times 10^5$ & $1.6 \times 10^5$ \\ 
1.0 & $1.1 \times 10^6$ & $2.0 \times 10^5$ \\ 
1.2 & $1.3 \times 10^6$ & $2.4 \times 10^5$ \\ 
1.4 & $1.5 \times 10^6$ & $2.8 \times 10^5$ \\
\end{tabular} 
\caption{{\bf Test Reynolds numbers.}Turbine diameter and approximate blade 
chord Reynolds numbers corresponding to tow speeds.} \label{tab:re}
\end{table}

>>>>

For example, the effect of Reynolds number on average power output was shown to
be significant on the 2 m Sandia Research Darrieus turbine in wind tunnel
testing \cite{Blackwell1976}: Maximum power coefficient, $C_{P,\mathrm{max}}$,
increased with Reynolds number, $Re_c$, along with a shift of the location of
$C_{P,\mathrm{max}}$ toward lower tip speed ratios due to delayed blade stall.
The effects of Reynolds number were quite dramatic over a relatively small range
of $Re_c \approx 1.1 \times 10^5$--$2.9 \times 10^5$. More recently, Bachant and
Wosnik \cite{Bachant2014, Bachant2015-RVAT-Re-dep} showed that turbine
performance and near-wake characteristics become Reynolds number independent at
$Re_c \approx 2 \times 10^5$.

@@

\begin{table}[ht]
\centering
\begin{tabular}{c|c|c}
Tow speed (m/s) & $Re_D$ & $Re_c$ at $\lambda = 3$ \\ 
\hline 
0.2 & $2.2 \times 10^5$ & $4.0 \times 10^4$ \\ 
0.4 & $4.3 \times 10^5$ & $8.0 \times 10^4$ \\ 
0.6 & $6.5 \times 10^5$ & $1.2 \times 10^5$ \\ 
0.8 & $8.6 \times 10^5$ & $1.6 \times 10^5$ \\ 
1.0 & $1.1 \times 10^6$ & $2.0 \times 10^5$ \\ 
1.2 & $1.3 \times 10^6$ & $2.4 \times 10^5$ \\ 
1.4 & $1.5 \times 10^6$ & $2.8 \times 10^5$ \\
\end{tabular} 
\caption{{\bf Test Reynolds numbers.} Turbine diameter and approximate blade 
chord Reynolds numbers corresponding to tow speeds.} \label{tab:re}
\end{table}
